---
title: "Basic Structures in onx"
author: "Eric Graves"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Basic Structures in onx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(onx)
```

The `onx` package is built on a foundation of basic structures that describe variable transformations. These structures
can be composed in interesting ways to describe how inputs map to outputs. Further, these structures are supported
by a set of generic methods allowing them to be manipulated consistently and intuitively.

The basic structures in `onx` are Bins, Levels, and Transforms

## Bins

Bins are the atomic units of transformations. A bin describes a mapping from an input to an output. The Bin class is 
abstract and iherited by four specialized types:

| Bin subtype | Description | Slots |
|------|------------------------------------------------|---------------|
| BinNumeric   | Describes a left-open & right-closed range for a numeric variable | `r slotNames("BinNumeric")` |
| BinFactor    | Maps a single character input | `r slotNames("BinFactor")` |
| BinException | Maps a single numeric input exactly | `r slotNames("BinException")` |
| BinMissing   | Maps `NA` values only | `r slotNames("BinMissing")` |

### Instantiating

All of the objects in this vignette should not be used directly. The following examples aim to demonstrate how `Bin`
objects work and should never need to directly implemented. Bins are instantiated differently depending on the type.

```{r}
n <- BinNumeric(lower=0, upper=10)

f <- BinFactor(level="cat")

e <- BinException(exception=-1)

m <- BinMissing()
```

All bins have a `show` method when printed to the console:

```{r}
show(n)
show(f)
show(e)
show(m)
```

### Combining

Some bins can be combined. Testing whether two bins can be combined is done using the `combinable` method.

```{r}
combinable(n, n)
combinable(f, f)
combinable(n, f)
combinable(n, e)
combinable(n, m)
```

Only `BinNumeric` are able to be combined. However they are only combined if their ranges overlap:

```{r}
A <- BinNumeric(lower=0, upper=20)
B <- BinNumeric(lower=10, upper=30)
C <- BinNumeric(lower=25, upper=50)

combinable(A, B)
combine(A, B) ## Combines and creates a single Bin with the new range

combinable(A, C)
combine(A, C) ## returns a list of the inputs

Reduce(combine, list(A, B, C))
Reduce(combine, list(A, C, B))

```

## Levels

## Transforms




